Relationship between solar wind, $D_{st}$, and plasmasphere mass density on one-hour time scales

### 2015-06-05 paper.tex

\section{Data}

For solar wind data, we use the \cite{Reconstruction}, which has a time coverage of 1972-2013.

Mass density data are from \cite{Denton}, which has a time coverage of 1980-1991 and is on a 15-minute time grid with many gaps.  A mean interpolation method was used to one-hour grid of the solar wind averages.  GIVE MORE DETAILS ABOUT THIS.  NEED ENOUGH INFORMATION TO BE ABLE TO REPRODUCE RESULTS GIVEN ONLY TWO DATA SETS.

@@

\begin{figure}[htp!]
\centering
(a)
\includegraphics[scale=0.7]{paperfigures/stormavs-dst.png}
(b)
\includegraphics[scale=0.7]{paperfigures/stormavs-mass.png}
\caption{(a) Average of solar wind and near-Earth measurements around the time D_${st}$ crossed below -40~nT onset. (b) Same as (a) except around time intervals where mass density crossed above $40 amu/cm^3$.  The bottom panel shows the number of mass density data points that were used for the average.}
\label{MassStorm}
\end{figure}
\clearpage

>>>>

\section{Data Preparation}
Starting from the data provided by \cite{Denton} for $\rho_{eq}$ and $F_{10.7}$ from 1980-1991, and \cite{Reconstruction} for all other variables from 1972-2013, the data were prepared to get all variables on the same consecutive time-grid. Since the latter was pre-adjusted to have data on a consecutive one-hour grid, the former variables were adjusted to be compatible. First, since the data covers multiple Geostationary Operational Environmental Satellites (GOES), one in particular (GOES 7) was selected to avoid overlapping data points.

Second, the various forms of "bad data" were converted from their respective set value to NaNs (e.g. 9999 becomes NaN). It was then condensed in range to match the time range from \cite{Reconstruction} down to the same start and end hours, and then interpolated from the GOES 15-minute grid to the one-hour grid by taking the median of all valid non-NaN data points within half an hour to either side of each hour. When no valid points existed in that hour period, a NaN was kept for the sake of the uniform time grid.

The only other point to note in this section: For finding storm times, all NaNs were linearly interpolated out of the data in order to aid in finding storms that may have had their onset point missing. Though this may skew the onset time slightly, it's thought to be less skewed than trying to determine start and end times with the NaNs in place. This interpolation was only used for determining storm times, and not for any analysis.

@@

\begin{figure}[htp!]
\centering
\includegraphics[scale=0.5]{paperfigures/stormavs-dst.eps}
\includegraphics[scale=0.5]{paperfigures/stormavs-mass.eps}
\caption{(a) Average of solar wind and near-Earth measurements around the time D_${st}$ crossed below -40~nT onset. (b) Same as (a) except around time intervals where mass density crossed above $40 amu/cm^3$.  The bottom panel shows the number of mass density data points that were used for the average.}
\label{MassStorm}
\end{figure}
\clearpage
